On the adhesivity of EGGS

### 2025-02-13 calco/main.tex
minima

Our result opens two threads of research. The first is to use the quasi-adhesivity of EGGS in order to
model their rewriting via the double-pushout (DPO) approach. This is likely to be straightforward, since 
the rules adopted in the literature of EGGS seems to be span of regular monos, and such rules
perfectly fit the mold of rewriting on quasi-adhesive categories. 
For example, the equivalence $x \div x = 1$, taken from the introductory example in~\cite{xxx}, 
can be modelled as the rule
\[to draw DPO rule\]

It still needs to be investigated what concurrency and termination, the key properties for DPO rewriting
on adhesive categories, 
means in the context of EGGS. More interestingly, another venue for development is using the adhesive 
machinery to extend the EGGS formalism. In fact, most of the results
presented here for hyper-graphs can be generalised to hierarchical hyper-graphs, that is, 
hypergraphs with a hierarchy (a partial order) among 
edges that is useful for adding structural information, such as encapsulation and sandboxing~\cite{xxx}.

>>>>

Our result opens two threads of research. The first is to use the quasi-adhesivity of EGGS in order to
model their rewriting via the double-pushout (DPO) approach. This seems to be straightforward, since 
the rules adopted in the literature of EGGS appears to be span of regular monos, and such rules
perfectly fit the mold of rewriting on quasi-adhesive categories. 
For example, the equivalence $x \div x = 1$, taken from the introductory example in~\cite{xxx}, 
can be modelled as the rule
\[to draw DPO rule\]

It still needs to be investigated what concurrency and termination, the key properties for DPO rewriting
on adhesive categories, 
mean in the context of EGGS. More interestingly, another venue for development is using the adhesive 
machinery to extend the EGGS formalism. In fact, most of the results
presented here for hyper-graphs can be generalised to hierarchical hyper-graphs, that is, 
hypergraphs with a hierarchy (a partial order) among 
edges that is useful for adding structural information, such as encapsulation and sandboxing~\cite{xxx}.
